Boosting Higgs Pair Production in the $b\bar{b}b\bar{b}$ Final State with Multivariate Techniques

### 2015-12-31 paper-arxiv-v1/sec-analysis.tex
Added v2 of paper in repo

  These jets are also constructed with the
  anti-$k_T$ clustering algorithm, now using a $R=1.2$ radius.
  %
  Large-$R$ jets are required to have
  $p_T \ge 200$~GeV and lie in a pseudo-rapidity region of
  $|\eta|<2.0$.
  %
  The more restrictive range  in pseudo-rapidity
  as compared to the small-$R$ jets
  is motivated by mimicking the  experimental requirements
  in ATLAS and CMS
  related to the track-jet based calibration~\cite{Aad:2014bia,ATLAS:2012kla}.

  In addition to the basic $p_T$ and $\eta$
  acceptance requirements, large-$R$ jets should also
  satisfy the  BDRS mass-drop tagger (MDT)~\cite{Butterworth:2008iy}
  conditions, where the {\tt FastJet} default
  parameters of  $\mu = 0.67$ and $y_{\textrm{cut}}= 0.09$ are used.
  %
  Before applying the BDRS tagger, the large-$R$ jet
  constituents are reclustered with the Cambridge/Aachen (C/A)
  algorithm~\cite{Dokshitzer:1997in,Wobisch:1998wt}
  with $R=1.2$.

@@

  These subjets are constructed by reclustering the constituents
  of a large-$R$ jet, again with the
  anti-$k_T$ algorithm,
  but this time with a smaller radius parameter, namely
  $R=0.3$~\cite{Aad:2015uka}. They are required to satisfy $p_T > 50$~GeV and $|\eta|<2.5$.
 %
  These small-$R$ subjets will be the main input for
  $b$-tagging in the boosted category.
  %
\end{itemize}

For the   boosted and intermediate categories,
which involve the use of large-$R$ jets,
we use jet substructure variables~\cite{Salam:2009jx,Aad:2013gja} to
improve the significance of the discrimination between signal and background
events in the MVA.
%
In particular we  consider the following jet
substructure variables:
\begin{itemize}
\item The $k_T$-splitting scale~\cite{Butterworth:2002tt,Butterworth:2008iy}.

@@

\item The ratio of 2-to-1 subjettiness $\tau_{12}$~\cite{Thaler:2010tr,Thaler:2011gf}.

@@

  The ratio of energy correlation functions $C_2^{(\beta)}$ is defined as
  \be
  \label{eq:c2}
C_2^{(\beta)} \equiv \frac{ {\rm ECF}(3,\beta) {\rm ECF}(1,\beta)}{\lc {\rm ECF}(2,\beta)\rc ^2} \, ,
\ee
while $D_2^{(\beta)}$ is instead defined as a double ratio of ECFs, that is
\be
e_3^{(\beta)}\equiv \frac{ {\rm ECF}(3,\beta)}{\lc {\rm ECF}(1,\beta)\rc^3} \, , \quad
  e_2^{(\beta)}\equiv \frac{ {\rm ECF}(2,\beta)}{\lc {\rm ECF}(1,\beta)\rc^2} \, , \quad
  \label{eq:d2}
D_2^{(\beta)} \equiv \frac{ e_3^{(\beta)})}{\lp e_2^{(\beta)} \rp^3} \, .
\ee
The energy correlation functions ${\rm ECF}(N,\beta)$ are defined
  in~\cite{Larkoski:2013eya} with the motivation that $(N+1)$-point correlators
  are sensitive to $N$-prong substructure.
  %
  The free parameter $\beta$ is set to a value of $\beta=2$,
  as recommended by the authors of Refs.~\cite{Larkoski:2013eya,Larkoski:2014gra}.
\end{itemize}

@@

The present analysis follows a strategy similar to the
scale-invariant resonance tagging of Ref.~\cite{Gouzevitch:2013qca}.
%
Rather than restricting to a specific event topology,
we aim to consistently combine the information from
the three possible topologies: boosted, intermediate and
resolved, with the optimal cuts for each category being determined
separately.
%
This approach is robust
under variations of
the underlying production model of Higgs pairs,
for instance in the case of
BSM dynamics, which can substantially increase
the degree of boost in the final state.

@@

Once a Higgs boson candidate has been identified,
its invariant mass is required to lie within a fixed window
of width $80~{\rm GeV}$ around the nominal Higgs boson mass of $m_h= 125$
GeV.
%
Specifically we require the condition
\be
\label{higgsmasswindow}
|m_{h,j} - 125| < 40~{\rm GeV} \, ,\, j=1,2 \, ,
\ee
where $m_{h,j}$ is the invariant mass of each of the two reconstructed  Higgs candidates.
%
This cut is substantially looser than the corresponding
cut used in the typical ATLAS and CMS $h\to b\bar{b}$
analyses~\cite{Aad:2012gxa,Chatrchyan:2013zna}.
%
The motivation
for such a loose cut 
is that further improvements of the
signal significance will be obtained using an MVA.
%
Only events where the two Higgs candidates satisfy
Eq.~(\ref{higgsmasswindow}) are classified as signal events.
%

@@

This is achieved as follows.
 %
First of all we perform an inclusive analysis, and optimise the
signal significance
$S/\sqrt{B}$ in each of the three categories separately, including
the MVA.
%
We find that the category with highest significance is
the boosted one,
followed by the intermediate and the resolved topologies, the latter two
with similar significance.
%
Therefore, when ascertaining which category an event is to be exclusively placed:
if the event satisfies the boosted requirements, it is assigned to
this category, else we check if it suits the intermediate
requirements.
%
It the event also fails the intermediate category
requirements, we
then check if it pass the resolved selection criteria.
%
The resulting exclusive event samples are then separately processed
through the MVA, allowing a consistent combination
of the significance of the three event categories.

@@

Another selection requirement for the boosted category is that the two
leading AKT03 subjets of the large-$R$ jet
should satisfy $p_T \ge $ 50 GeV.
%
To motivate this cut, in Fig.~\ref{fig:cutplots22}
we show the distribution in $p_T$ of the leading
and subleading AKT03 subjets in the subleading large-$R$ jet in events
corresponding to the boosted category.
%
It is clear from the comparison that the subjet $p_T$ spectrum is
relatively harder in the signal with respect to the background.
%
On the other hand, considering the subleading AKT03 subjet,
this cut in $p_T$
cannot be too harsh, to maintain a high signal selection
efficiency.
%
Therefore,
as for the previous distribution, also here 
a compromise between suppressing backgrounds but keeping a large fraction of
signal events is crucial.

@@

We shall now investigate the discrimination power
provided by jet substructure
quantities.
%
In Fig.~\ref{fig:mva_substructure_1}
we show the distributions of representative
 substructure variables for the boosted category: the
$k_t$ splitting scale $\sqrt{d_{12}}$, Eq.~(\ref{eq:ktsplitting}), 
the ECF ratio $C_2^{(\beta)}$,
Eq.~(\ref{eq:c2}), and
the 2--to--1 subjettiness ratio $\tau_{12}$, Eq.~(\ref{eq:tau21}),
all for the leading
Higgs candidates, and also $\tau_{12}$ for the subleading
Higgs candidates.

@@

From Fig.~\ref{fig:mva_substructure_1}
we observe how for these substructure variables the shapes of the signal
and background distributions reflect
the inherent differences in the internal structure of
QCD jets and jets originating from Higgs decays.
%
Signal and background distributions peak
in rather
different regions. For example, the $k_t$ splitting scale $\sqrt{d_{12}}$
peaks around 80 GeV (40 GeV) for signal (background) events, while
the distribution of the
ECF ratio $C_2^{(\beta)}$ is concentrated at small values
for signal and is much broader for background events.
%
From Fig.~\ref{fig:mva_substructure_1} we also see
the distributions of the subjettiness ratio $\tau_{12}$ are
reasonably similar
for both the leading and the subleading jets.
%

@@

Now we turn to discuss how the description of kinematic
distributions for $hh\to 4b$ signal
and background processes are
modified in the presence of pileup.
%
To study the impact of PU,
Minimum Bias events have been generated
with {\tt Pythia8}, and then
superimposed to the signal
and background samples described in Sect.~\ref{mcgeneration}.
%
We have explored two scenarios,
one with a mean number of
PU vertices per bunch crossing of $\la n_{\rm PU}\ra=80$,
and another
with $\la n_{\rm PU}\ra=150$.
%
While the latter is closer to the HL-LHC forecasts,
we adopt $\la n_{\rm PU}\ra=80$ as our baseline,
given that it
is beyond the scope of this paper to fully optimize
the PU subtraction.

%
In order to subtract PU in hadronic collisions, a number of techniques
are available~\cite{Cacciari:2009dp,TheATLAScollaboration:2013pia,Butterworth:2008iy,Cacciari:2007fd,Krohn:2009th,Krohn:2013lba,Cacciari:2008gd,Ellis:2009me,Bertolini:2014bba,Cacciari:2014gra,Cacciari:2014jta,Berta:2014eza,Larkoski:2014wba}.\footnote{
These techniques have also important applications in the subtraction
of the UE/MPI contamination for jet reconstruction
in heavy ion collisions~\cite{Cacciari:2010te}.
}
%
In this work, PU  is subtracted
with the {\tt SoftKiller} (SK)
method~\cite{Cacciari:2014gra}, as implemented in {\tt FastJet},
whose performance has been shown to
improve the commonly used area-based subtraction~\cite{Cacciari:2009dp}.
%
The idea underlying {\tt SoftKiller} consists of eliminating particles
below a given cut-off in their transverse momentum, $p_T^{\rm (cut)}$, whose
value is dynamically determined in a way that makes the event-wide
transverse-momentum flow density $\rho$ vanish.
%
This $p_T$ flow density is defined as
\be
\rho\equiv{\rm median}_i \Bigg\{ \frac{p_{Ti}}{A_i}\Bigg\} \, ,
\ee
where the median is computed over all the regions $i$ with area
$A_i$ and transverse momentum $p_{Ti}$ in which the $\lp \eta,\phi\rp$ plane
is partitioned.

From its definition in terms of the median,
it follows that the value of $p_T^{(\rm cut)}$
will be dynamically raised until half of the regions have
$p_{Ti}=0$.
%
The size and number of these regions is a free parameter of the algorithm -
here we will use square regions with length $a=0.4$.
%
We restrict ourselves to the central rapidity region,
$|\eta| \le 2.5$, for the estimation of the
$p_T$ flow density $\rho$.
%
The {\tt SoftKiller} subtraction is applied to particles at the end of the parton shower, before
jet clustering.

In addition, jet trimming~\cite{Krohn:2009th}, as implemented in {\tt FastJet}, is applied to large-$R$ jets.
%
The trimming parameters are chosen such that the constituents of a given jet are reclustered into $k_T$ subjets with $R_{\textrm{sub}} = 0.2$.
Subjets with transverse momentum less than 5\% of the total
transverse momentum of the large-$R$ jet are then removed.
%
The use of trimming in addition to PU removal with {\tt SoftKiller} is necessary to correct the jet mass in the boosted category,
which is particularly susceptible
to soft, wide-angle contaminations.
%
No trimming is applied to the small-$R$ jets.

%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
  \begin{center}
    \includegraphics[width=0.49\textwidth]{plots/m_htot_res_signal_PUnoSK.pdf}
    \includegraphics[width=0.49\textwidth]{plots/m_htot_bst_signal_PUnoTrim.pdf}
    \caption{\small
    The invariant mass distributions of Higgs candidates in signal
    events in the resolved (left) and boosted
    (right) categories.
    %
    In the resolved category,
    we compare  the results without PU
    with those with PU $\la n_{\rm PU}\ra=80$,
    with and without SK subtraction.
    %
    In the boosted case, the comparison is between no PU,
    PU with only SK subtraction,
    and PU with both SK and trimming.
}
\label{fig:PUvalidation}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%

%
In Fig.~\ref{fig:PUvalidation} we show the
invariant mass distributions of the
Higgs candidates for signal
events in the resolved and boosted categories.
%
 In the resolved category,
    we compare  the results without PU
    with those with PU $\la n_{\rm PU}\ra=80$,
    with and without SK subtraction.
    %
    If PU is not subtracted, there is a large shift in the Higgs mass
peak, by more than 30 GeV.
%
Once SK subtraction is performed, we recover a distribution much closer
to the no PU case, with only a small shift of $\simeq 5$ GeV
and a broadening of the mass
distribution.
    %
    In the boosted case, the comparison is performed between no PU,
    PU with only SK subtraction,
    and PU with both SK and trimming.
%
We find that
the mass distribution for jets to which no trimming
is applied peaks at around 160~GeV, even
after PU subtraction with {\tt SoftKiller}.
%
When trimming is applied in addition to {\tt SoftKiller}, 
the distribution peaks close to the nominal Higgs mass.

In Fig.~\ref{fig:mHH_PU}
we compare the transverse momentum of the leading Higgs
candidate, $p_t^{h}$ and the invariant mass of the di-Higgs system
$m_{hh}$, in both the boosted and resolved categories.
%
In the case of the $p_T^{h}$ distribution, the differences between the selection
criteria for the resolved
and boosted categories is reflected in the rightward shift of the latter.
%
After subtraction,
the effects of PU are small in the two categories.
%
A similar behaviour is observed in the di-Higgs invariant mass distribution.
%
We can also assess the impact of PU in some of
substructure variables that will be 
used as input to the MVA in the boosted category.
%
In Fig.~\ref{fig:Substructure_PU} we show the 2-to-1 subjettiness ratio
$\tau_{21}$, Eq.~(\ref{eq:tau21}), and the ratio
of energy correlation functions, $C_2^{(\beta)}$,
Eq.~(\ref{eq:c2}), for the leading Higgs candidate.
%
We observe that
the shapes of both substructure variables
are reasonably robust in a environment including PU.
%
Therefore we can consider the PU subtraction strategy
as validated for the purposes of this study, although
further optimisation should still be possible, both
for the trimming and for the {\tt SoftKiller}
input settings.

%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
  \begin{center}
  \includegraphics[width=0.49\textwidth]{plots/pt_H0_C2_res_comp.pdf}
  \includegraphics[width=0.49\textwidth]{plots/pt_H0_C2_bst_comp.pdf}
  \includegraphics[width=0.49\textwidth]{plots/m_HH_C2_res_comp.pdf}
  \includegraphics[width=0.49\textwidth]{plots/m_HH_C2_bst_comp.pdf}
  \caption{\small
   The
   transverse momentum $p_T^h$ of the leading
    Higgs candidate (upper plots) and of the invariant mass $m_{hh}$
    of the di-Higgs system (lower plots) in the resolved
    (left) and boosted (right) categories.
    %
    We compare the results without PU with those with PU,
    for $\la n_{\rm PU}\ra=80$ and SK+Trim subtraction,
    as explained in the text.
}
\label{fig:mHH_PU}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%

@@

It is illustrative to determine
the mass resolution obtained for the
reconstructed Higgs candidates in the various cases.
%
In Table~\ref{tab:massresolution}
we indicate the shift of the invariant mass peak as compared
to the nominal Higgs mass, $\la m_h^{\rm reco}\ra-m_h$,
and the corresponding width of the distribution, $\sigma_{m_h}$,
obtained from fitting a Gaussian to the mass distributions
of both the leading and subleading Higgs candidates in
the resolved category.
        %
        We show results for three cases: without PU, with PU $\la n_{\rm PU}\ra=80$
        but without subtraction (only for the
        resolved category), and the same with SK(+Trim) subtraction.

        In both categories,
        we find a mass resolution of around 9 GeV in the case
        without PU.
        %
        In the case of PU
        with SK(+Trim) subtraction,
        in the resolved category the mass resolution
        worsens only slightly
        to around 11 GeV, while in the boosted category we find
        the same resolution as in the no PU case.
        %
        We also note that after SK(+Trim) subtraction, the peak of
        the invariant mass distributions of Higgs candidates
        coincides with the nominal values of $m_h$ within a few GeV.

>>>>

  These jets are also constructed with the
  anti-$k_T$ clustering algorithm, now using a $R=1.0$ radius.
  %
  Large-$R$ jets are required to have
  $p_T \ge 200$~GeV and lie in a pseudo-rapidity region of
  $|\eta|<2.0$.
  %
  The more restrictive range  in pseudo-rapidity
  as compared to the small-$R$ jets
  is motivated by mimicking the  experimental requirements
  in ATLAS and CMS
  related to the track-jet based calibration~\cite{Aad:2014bia,ATLAS:2012kla}.

  In addition to the basic $p_T$ and $\eta$
  acceptance requirements, large-$R$ jets should also
  satisfy the  BDRS mass-drop tagger (MDT)~\cite{Butterworth:2008iy}
  conditions, where the {\tt FastJet} default
  parameters of  $\mu_{\rm mdt} = 0.67$ and $y_{\rm mdt}=0.09$ are used.
  %
  Before applying the BDRS tagger, the large-$R$ jet
  constituents are reclustered with the Cambridge/Aachen (C/A)
  algorithm~\cite{Dokshitzer:1997in,Wobisch:1998wt}
  with $R=1.0$.

  In the case of the analysis including PU, a trimming
  algorithm~\cite{Krohn:2009th}
  is applied to all large-$R$ jets to mitigate the effects of PU,
  especially on the jet mass.
  %
  For further details see Sect.~\ref{sec:pileup}.

@@

 All final-state particles are clustered using the
 anti-$k_T$ algorithm, but this time with
 a smaller radius parameter, namely $R=0.3$.
 %
 The resulting anti-$k_T$ $R=0.3$ (AKT03) jets
 are then ghost-associated to each large-$R$ jets
 in order to define its subjets~\cite{Aad:2015uka}.

 These AKT03 subjets
  are required to satisfy
  $p_T > 50$~GeV and $|\eta|<2.5$, and
   will be the main input for
  $b$-tagging in the boosted category.
  %
\end{itemize}

For the   boosted and intermediate categories,
which involve the use of large-$R$ jets,
we use jet substructure variables~\cite{Salam:2009jx,Aad:2013gja} to
improve the significance of the discrimination between signal and background
events in the MVA.
%
In particular we  consider the following
substructure variables:
\begin{itemize}
\item The $k_T$-splitting scale~\cite{Butterworth:2002tt,Butterworth:2008iy}.

@@

\item The ratio of 2-to-1 subjettiness $\tau_{21}$~\cite{Thaler:2010tr,Thaler:2011gf}.

@@

  The ratio of energy correlation functions $C_2^{(\beta)}$ is defined as
  \be
  \label{eq:c2}
C_2^{(\beta)} \equiv \frac{ {\rm ECF}(3,\beta) {\rm ECF}(1,\beta)}{\lc {\rm ECF}(2,\beta)\rc ^2} \, ,
\ee
while $D_2^{(\beta)}$ is instead defined as a double ratio of ECFs, that is,
\be
e_3^{(\beta)}\equiv \frac{ {\rm ECF}(3,\beta)}{\lc {\rm ECF}(1,\beta)\rc^3} \, , \quad
  e_2^{(\beta)}\equiv \frac{ {\rm ECF}(2,\beta)}{\lc {\rm ECF}(1,\beta)\rc^2} \, , \quad
  \label{eq:d2}
D_2^{(\beta)} \equiv \frac{ e_3^{(\beta)})}{\lp e_2^{(\beta)} \rp^3} \, .
\ee
The energy correlation functions ${\rm ECF}(N,\beta)$ are defined
  in~\cite{Larkoski:2013eya} with the motivation that $(N+1)$-point correlators
  are sensitive to $N$-prong substructure.
  %
  The free parameter $\beta$ is set to a value of $\beta=2$,
  as recommended by Refs.~\cite{Larkoski:2013eya,Larkoski:2014gra}.
\end{itemize}

@@

The present analysis follows a strategy similar to the
scale-invariant resonance tagging of Ref.~\cite{Gouzevitch:2013qca}.
%
Rather than restricting ourselves to a specific event topology,
we aim to consistently combine the information from
the three possible topologies: boosted, intermediate and
resolved, with the optimal cuts for each category being determined
separately.
%
This approach is robust
under variations of
the underlying production model of Higgs pairs,
for instance in the case of
BSM dynamics, which can substantially increase
the degree of boost in the final state.

@@

Once a Higgs boson candidate has been identified,
its invariant mass is required to lie within a fixed window
of width $80~{\rm GeV}$ around the nominal Higgs boson mass of $m_h= 125$
GeV.
%
Specifically we require the condition
\be
\label{higgsmasswindow}
|m_{h,j} - 125~{\rm GeV}| < 40~{\rm GeV} \, ,\, j=1,2 \, ,
\ee
where $m_{h,j}$ is the invariant mass of each of the two reconstructed  Higgs candidates.
%
This cut is substantially looser than the corresponding
cut used in the typical ATLAS and CMS $h\to b\bar{b}$
analyses~\cite{Aad:2012gxa,Chatrchyan:2013zna}.
%
The motivation
for such a loose cut 
is that further improvements of the
signal significance will be obtained using an MVA.
%
Only events where the two Higgs candidates satisfy
Eq.~(\ref{higgsmasswindow}) are classified as signal events.
%

@@

This is achieved as follows.
 %
First of all we perform an inclusive analysis, and optimise the
signal significance
$S/\sqrt{B}$ in each of the three categories separately, including
the MVA.
%
We find that the category with highest significance is
the boosted one,
followed by the intermediate and the resolved topologies, the latter two
with similar significance.
%
Therefore, when ascertaining in
which category an event is to be exclusively placed:
if the event satisfies the boosted requirements, it is assigned to
this category, else we check if it suits the intermediate
requirements.
%
If the event also fails the intermediate category
requirements, we
then check if it passes the resolved selection criteria.
%
The resulting exclusive event samples are then separately processed
through the MVA, allowing for a consistent combination
of the significance of the three event categories.

@@

Another selection requirement for the boosted category is that the two
leading AKT03 subjets of the large-$R$ jet
should satisfy $p_T \ge $ 50 GeV.
%
To motivate this cut, in Fig.~\ref{fig:cutplots22}
we show the distribution in $p_T$ of the leading
and subleading AKT03 subjets in the subleading large-$R$ jet in events
corresponding to the boosted category.
%
It is clear from the comparison that the subjet $p_T$ spectrum is
relatively harder in the signal with respect to the background.
%
On the other hand, considering the subleading AKT03 subjet,
this cut in $p_T$
cannot be too harsh, to maintain a high signal selection
efficiency.
%
Therefore,
as for the previous distribution, the chosen cut value is
a compromise between suppressing backgrounds but keeping a large fraction of
signal events is crucial.

@@

We shall now investigate the discrimination power
provided by jet substructure
quantities.
%
In Fig.~\ref{fig:mva_substructure_1}
we show the distributions of representative
 substructure variables for the boosted category: the
$k_t$ splitting scale $\sqrt{d_{12}}$, Eq.~(\ref{eq:ktsplitting}), 
the ECF ratio $C_2^{(\beta)}$,
Eq.~(\ref{eq:c2}), and
the 2--to--1 subjettiness ratio $\tau_{21}$, Eq.~(\ref{eq:tau21}),
all for the leading
Higgs candidates, and also $\tau_{21}$ for the subleading
Higgs candidates.

@@

From Fig.~\ref{fig:mva_substructure_1}
we observe how for these substructure variables the shapes of the signal
and background distributions reflect
the inherent differences in the internal structure of
QCD jets and jets originating from Higgs decays.
%
Signal and background distributions peak
in rather
different regions. For example, the $k_t$ splitting scale $\sqrt{d_{12}}$
peaks around 80 GeV (40 GeV) for signal (background) events, while
the distribution of the
ECF ratio $C_2^{(\beta)}$ is concentrated at small values
for signal and is much broader for background events.
%
From Fig.~\ref{fig:mva_substructure_1} we also see
the distributions of the subjettiness ratio $\tau_{21}$ are
reasonably similar
for both the leading and the subleading jets.
%

@@

Now we turn to discuss how the description of kinematic
distributions for signal
and background processes are
modified in the presence of pileup.
%
To study the impact of PU,
Minimum Bias events have been generated
with {\tt Pythia8}, and then
superimposed to the signal
and background samples described in Sect.~\ref{mcgeneration}.
%
We have explored two scenarios,
one with a number of
PU vertices per bunch crossing of $n_{\rm PU}=80$,
and another
with $n_{\rm PU}=150$.
%
In the following we adopt $n_{\rm PU}=80$ as our baseline,
and denote this scenario by PU80.
%
We have verified that the combined signal significance is
similar if $n_{\rm PU}=150$ is adopted instead.

%
In order to subtract PU in hadronic collisions, a number of techniques
are available~\cite{Cacciari:2009dp,TheATLAScollaboration:2013pia,Butterworth:2008iy,Cacciari:2007fd,Krohn:2009th,Krohn:2013lba,Cacciari:2008gd,Ellis:2009me,Bertolini:2014bba,Cacciari:2014gra,Cacciari:2014jta,Berta:2014eza,Larkoski:2014wba}.\footnote{
These techniques have also important applications in the subtraction
of the UE/MPI contamination for jet reconstruction
in heavy ion collisions~\cite{Cacciari:2010te}.
}
%
In this work, PU  is subtracted
with the {\tt SoftKiller} (SK)
method~\cite{Cacciari:2014gra}, as implemented in {\tt FastJet},
whose performance has been shown to
improve the commonly used area-based subtraction~\cite{Cacciari:2009dp}.
%
The idea underlying {\tt SoftKiller} consists of eliminating particles
below a given cut-off in their transverse momentum, $p_T^{\rm (cut)}$, whose
value is dynamically determined so that the event-wide
transverse-momentum flow density $\rho$ vanishes, where $\rho$ is
defined as
\be
\rho\equiv{\rm median}_i \Bigg\{ \frac{p_{Ti}}{A_i}\Bigg\} \, ,
\ee
and where the median is computed over all the regions $i$ with area
$A_i$ and transverse momentum $p_{Ti}$ in which the $\lp \eta,\phi\rp$ plane
is partitioned.

From its definition in terms of the median,
it follows that the value of $p_T^{(\rm cut)}$
will be dynamically raised until half of the regions have
$p_{Ti}=0$.
%
The size and number of these regions is a free parameter of the algorithm -
here we will use square regions with length $a=0.4$.
%
We restrict ourselves to the central rapidity region,
$|\eta| \le 2.5$, for the estimation of the
$p_T$ flow density $\rho$.
%
The {\tt SoftKiller} subtraction is then
applied to particles at the end of the parton shower, before
jet clustering.

In addition, jet trimming~\cite{Krohn:2009th}, as implemented in {\tt FastJet}, is applied to large-$R$ jets.
%
The trimming parameters are chosen such that the constituents of a given jet are reclustered into $k_T$ subjets with $R_{\textrm{sub}} = 0.2$.
Subjets with transverse momentum less than 5\% of the total
transverse momentum of the large-$R$ jet are then removed.
%
The use of trimming in addition to PU removal with {\tt SoftKiller} is necessary to correct the jet mass in the boosted category,
which is particularly susceptible
to soft, wide-angle contaminations.
%
No trimming is applied to the small-$R$ jets and
to the case without PU.

%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
  \begin{center}
    \includegraphics[width=0.49\textwidth]{plots/m_htot_res_signal_PUnoSK.pdf}
    \includegraphics[width=0.49\textwidth]{plots/m_htot_bst_signal_PUnoTrim.pdf}
    \caption{\small
    The invariant mass distributions of Higgs candidates in signal
    events in the resolved (left) and boosted
    (right) categories.
    %
    In the resolved category,
    we compare  the results without PU
    with those with PU80
    with and without SK subtraction.
    %
    In the boosted case, the comparison is performed between no PU,
    PU with only SK subtraction,
    and PU with both SK and trimming.
}
\label{fig:PUvalidation}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%

%
In Fig.~\ref{fig:PUvalidation} we show the
invariant mass distributions of the
Higgs candidates for signal
events in the resolved and boosted categories.
%
 In the resolved category,
    we compare  the results without PU
    with those with PU80, with and without SK subtraction.
    %
    If PU is not subtracted, there is a large shift in the Higgs mass
peak, by more than 30 GeV.
%
Once SK subtraction is performed, we recover a distribution much closer
to the no PU case, with only a small shift of a few GeV
and a broadening of the mass
distribution.
    %
    In the boosted case, the comparison is performed between no PU,
    PU with only SK subtraction,
    and PU with both SK and trimming.
%
We find that
the mass distribution for jets to which no trimming
is applied peaks at around 160~GeV, even
after PU subtraction with {\tt SoftKiller}.
%
When trimming is applied in addition to {\tt SoftKiller}, 
the distribution peaks close to the nominal Higgs mass, as in the case
of the resolved category.

In Fig.~\ref{fig:mHH_PU}
we compare the transverse momentum of the leading Higgs
candidate, $p_t^{h}$ and the invariant mass of the di-Higgs system
$m_{hh}$, in both the boosted and resolved categories,
between the no PU and the PU+SK+Trim cases.
%
In the case of the $p_T^{h}$ distribution, the differences between the selection
criteria for the resolved
and boosted categories is reflected in the rightward shift of the latter.
%
After subtraction,
the effects of PU are small in the two categories.
%
A similar behaviour is observed in the di-Higgs invariant mass distribution.

We can also assess the impact of PU on the
substructure variables that will be 
used as input to the MVA in the boosted
and intermediate categories.
%
In Fig.~\ref{fig:Substructure_PU} we show the 2-to-1 subjettiness ratio
$\tau_{21}$, Eq.~(\ref{eq:tau21}), and the ratio
of energy correlation functions $C_2^{(\beta)}$,
Eq.~(\ref{eq:c2}), for the leading Higgs candidate.
%
We observe that
the shapes of both substructure variables
are reasonably robust in a environment including significant PU.
%
Therefore we can consider the PU subtraction strategy
as validated for the purposes of this study, although
further optimisation should still be possible, both in terms of
the {\tt SoftKiller} and of the trimming
input settings.

%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[t]
  \begin{center}
  \includegraphics[width=0.49\textwidth]{plots/pt_H0_C2_res_comp.pdf}
  \includegraphics[width=0.49\textwidth]{plots/pt_H0_C2_bst_comp.pdf}
  \includegraphics[width=0.49\textwidth]{plots/m_HH_C2_res_comp.pdf}
  \includegraphics[width=0.49\textwidth]{plots/m_HH_C2_bst_comp.pdf}
  \caption{\small
   The
   transverse momentum $p_T^h$ of the leading
    Higgs candidate (upper plots) and of the invariant mass $m_{hh}$
    of the di-Higgs system (lower plots) in the resolved
    (left) and boosted (right) categories.
    %
    We compare the results without PU with those with PU80
    and SK+Trim subtraction,
    as explained in the text.
}
\label{fig:mHH_PU}
\end{center}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%

@@

 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
    \begin{table}[h]
      \centering
      \begin{tabular}{|c|c|c|c|}
        \hline
        \multicolumn{4}{|c|}{Resolved category}\\
        \hline
        \hline
        &   &   $\la m_h^{\rm reco}\ra-m_h$  &  $\sigma_{m_h}$  \\
              \hline
        \multirow{2}{*}{no PU}  & leading $h$  &  -3.8 GeV   & $\lp 8.5\pm 0.2\rp$ GeV   \\
          & subleading $h$   & -5.8 GeV  &  $\lp 9.1\pm 0.3\rp$ GeV \\
        \hline
          \multirow{2}{*}{PU80}  & leading $h$  &  +33 GeV   & $\lp 8.8\pm 1.5\rp$ GeV   \\
          & subleading $h$   & +31 GeV  &  $\lp 11.7\pm 3.3\rp$ GeV \\
          \hline
            \multirow{2}{*}{PU80+SK}  & leading $h$  &  +3.9 GeV   & $\lp 10.7\pm 0.3\rp$ GeV   \\
          & subleading $h$   & +2.1 GeV  &  $\lp 10.5\pm 0.3\rp$ GeV \\
            \hline
            \multicolumn{4}{c}{}\\
             \hline
        \multicolumn{4}{|c|}{Boosted category}\\
        \hline
        \hline
        &   &   $\la m_h^{\rm reco}\ra-m_h$  &  $\sigma_{m_h}$  \\
              \hline
        \multirow{2}{*}{no PU}  & leading $h$  &  +2.0 GeV   & $\lp 8.2\pm 0.5\rp$ GeV   \\
          & subleading $h$   & +1.0 GeV  &  $\lp 8.8\pm 0.5\rp$ GeV \\
        \hline
              \multirow{2}{*}{PU80+SK+Trim}  & leading $h$  &  -2.2 GeV   & $\lp 8.7\pm 0.7\rp$ GeV   \\
          & subleading $h$   & -4.9 GeV  &  $\lp 9.0\pm 0.8 \rp$ GeV \\
        \hline
        \end{tabular}
      \caption{\label{tab:massresolution}
        Resolution of the invariant mass distribution of
        reconstructed Higgs candidates in the resolved 
        and boosted  categories.
        %
        We show three cases: no PU, with PU80
        without subtraction (only for resolved),
        and the same with SK+Trim subtraction.
        %
        We indicate the shift of the fitted invariant
        mass peak $\la m_h^{\rm reco}\ra$ for
        the Higgs candidates as compared
        to the nominal Higgs mass $m_h$, as well as the
        the fitted  Gaussian  width  $\sigma_{m_h}$.
        }
    \end{table}
    %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

It is illustrative to determine
the mass resolution obtained for the
reconstructed Higgs candidates in the various cases considered in
the present study.
%
In Table~\ref{tab:massresolution}
we indicate the shift of the fitted invariant mass peak as compared
to the nominal Higgs mass, $\la m_h^{\rm reco}\ra-m_h$,
and the corresponding width of the distribution, $\sigma_{m_h}$,
obtained from fitting a Gaussian to the mass distributions
of leading and subleading Higgs candidates in
the resolved and boosted categories.
        %
        We show results for three cases: without PU, with PU80
        but without subtraction (only for the
        resolved category), and the same with SK+Trim subtraction.

        In both categories,
        we find a mass resolution of around 9 GeV in the case
        without PU.
        %
        In the case of PU
        with SK+Trim subtraction,
        in the resolved category the mass resolution
        worsens only slightly
        to around 11 GeV, while in the boosted category we find
        the same resolution as in the no PU case.
        %
        We also note that after SK+Trim subtraction, the peak of
        the invariant mass distributions of Higgs candidates
        coincides with the nominal values of $m_h$ within a few GeV
        for the two categories.
